---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## Step 1 Result

```{r}
library(classdata)
str(ames)
#?ames
```
Variables in ames dataset:

Parcel ID: character with ID (int)
Address: property address (str)
Style: factor variable in type of housing (str)
Occupancy: factor variable in type of housing (str)
Sale Date: date of sale (date)
Sale Price: sales price (int)
Multi Sale: was this sale part of a package? (bool)
YearBuilt: year in which house was built (int)
Acres: acres of the lot (double)
TotalLivingArea (sf): total living area in square feet (int)
Bedrooms: num of bedrooms (int)
FinishedBsmtArea (sf): total area of finished basement (int)
LotArea (sf): total lot area (int)
AC: does the property have AC? (bool)
FirePlace: does the property have a fireplace? (bool)
Neighborhood: factor variable to indicate neighborhood (str)


## Step 2 Result
Main variable: Sale Price. We will focus on this variable.

## Step 3 Result
```{r range}
data(ames)
range(ames$`Sale Price`)

library(ggplot2)
ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 100000, position="stack")
```

The histogram shows that most of the data is concentrated on the left side of the graph, with some outliers on the right side. This shows that the distribution of Sale Price is not uniform.

## Step 4 Result
### Chaitanya's Work: 
```{r TotalLivingArea}
# range
range(ames$`TotalLivingArea (sf)`, na.rm = TRUE)
# histogram
hist(ames$`TotalLivingArea (sf)`,
     main = "Distribution of Total Living Area",
     xlab = "Total Living Area (sq ft)",
     col = "lightblue")
# scatterplot with Sale Price
plot(ames$`TotalLivingArea (sf)`, ames$`Sale Price`,
     main = "Sale Price vs Total Living Area",
     xlab = "Total Living Area (sq ft)",
     ylab = "Sale Price",
     pch = 19,
     col = "pink")
```
Summary: The variable TotalLivingArea (sf) represents the total living space of a house in square feet. The values range from about 0 to around 6000 square feet. The histogram shows that most houses have living areas between 1000 and 2000 square feet, with fewer houses having very large living areas. The distribution is slightly right-skewed because a small number of houses have much larger living areas.

The scatterplot comparing TotalLivingArea and Sale Price does not show a clear positive trend because many houses have a Sale Price of 0, which creates a horizontal cluster of points near the bottom of the plot. These values are likely missing or incorrect data entries, which makes the relationship harder to see. If those values were removed, we would expect larger houses to generally have higher sale prices.

### Kalyna's Work:
```{r}
data(ames)
#Range
range(ames$`FinishedBsmtArea (sf)`)

library(ggplot2)
#Histogram distribution
ggplot(ames, aes(x = `FinishedBsmtArea (sf)`)) +
geom_histogram(binwidth = 250)

#Scatterplot comparison
ggplot(ames, aes(x = `FinishedBsmtArea (sf)`, y = `Sale Price`)) +
geom_point() +
scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
scale_y_continuous(labels = scales::label_number(accuracy = 1)) +
scale_y_continuous(limits = c(0, 1250000))
```
Summary: The variable FinishedBsmtArea (sf) shows the square footage of the basements of each home. The histogram distribution shows a peak at around 1000 sqare feet, with a few outliers around the 3500 and 6500 marks. The scatterplot shows that the two variables have a moderate positive correlation. There are a few noticeable outliers, and a "floor" of points, since many of the houses are listed at a sale price of 0.


### Mariana's Work:
```{r code 1}
sum(ames$YearBuilt == 0, na.rm = TRUE)

range(ames$`YearBuilt`, na.rm = TRUE)
library(dplyr)
ames_clean <- ames %>% filter(YearBuilt > 0)
range(ames_clean$YearBuilt)
ggplot(ames, aes(x = `YearBuilt`)) +
  geom_histogram(binwidth = 5, position="stack") +
  coord_cartesian(xlim = c(1880, 2022))
```

It looks like there are more houses built on the second half of the range of the graph (1960-2022). It shows an average increase throughout the years.

```{r code 2}
ggplot(ames_clean, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_point()
```

To better see the relationship, I adjusted the Sale Price axis. 

```{r code 3}
ggplot(ames_clean, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_point() +
  coord_cartesian(ylim = c(0, 750000))
```

Generally, it seems like sales price increases with the year the house is built. So new houses in Ames generally have higher sale prices.
The oddities seen in step 3 can be seen in the first plot, as some outlier values are seen for very high sale prices. These outliers are around year 2000, following the trend that newer houses usually have higher sale prices.

### Sebastian's Work:
I choose to work with the variable 'LotArea(sf)'.
```{r LotArea(sf)}
library(ggplot2)
# Range
range(ames$`LotArea(sf)`, na.rm = TRUE)
# Histogram
ggplot(ames, aes(x = `LotArea(sf)`)) +
  geom_histogram(binwidth = 30, position="stack") +
  coord_cartesian(xlim = c(0, 50000))
# Scatterplot with Sale Price
ggplot(ames, aes(x = `LotArea(sf)`, y = `Sale Price`)) +
geom_point() +
scale_x_continuous(labels = scales::label_number(accuracy = 1)) +
scale_y_continuous(labels = scales::label_number(accuracy = 1)) +
scale_y_continuous(limits = c(0, 750000))
```

Summary: LotArea(sf) represents the total horizontal surface area within a property's boundary lines in Ames, measured in square feet. The values range from about 0 to around 6000 square feet. The histogram shows that the vast majority of lot areas for homes in Ames are around 10000 (or less) square feet, with much fewer houses having very large lot areas (>3000 sq ft). The distribution is right-skewed because of how little the number of houses with larger lot areas compare to those with lot areas around 10000 sq ft, which are concentrated to the left of the histogram.

The scatterplot highlights how there are not many outliers in the first place, but there are a few with extremely large lot areas (a few measured between 200000 and 600000 sq ft, which are several acres of land).


