---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## Step 1 Result

```{r}
library(classdata)
str(ames)
#?ames
```
Variables in ames dataset:

Parcel ID: character with ID (int)
Address: property address (str)
Style: factor variable in type of housing (str)
Occupancy: factor variable in type of housing (str)
Sale Date: date of sale (date)
Sale Price: sales price (int)
Multi Sale: was this sale part of a package? (bool)
YearBuilt: year in which house was built (int)
Acres: acres of the lot (double)
TotalLivingArea (sf): total living area in square feet (int)
Bedrooms: num of bedrooms (int)
FinishedBsmtArea (sf): total area of finished basement (int)
LotArea (sf): total lot area (int)
AC: does the property have AC? (bool)
FirePlace: does the property have a fireplace? (bool)
Neighborhood: factor variable to indicate neighborhood (str)


## Step 2 Result
Main variable: Sale Price. We will focus on this variable.

## Step 3 Result
```{r range}
data(ames)
range(ames$`Sale Price`)

library(ggplot2)
ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 100000, position="stack")
```

The histogram shows that most of the data is concentrated on the left side of the graph, with some outliers on the right side. This shows that the distribution of Sale Price is not uniform.

## Step 4 Result
### Chaitanya's Work:


### Kalyna's Work:


### Mariana's Work:
```{r code 1}
sum(ames$YearBuilt == 0, na.rm = TRUE)

range(ames$`YearBuilt`, na.rm = TRUE)
library(dplyr)
ames_clean <- ames %>% filter(YearBuilt > 0)
range(ames_clean$YearBuilt)
ggplot(ames, aes(x = `YearBuilt`)) +
  geom_histogram(binwidth = 5, position="stack") +
  coord_cartesian(xlim = c(1880, 2022))
```

It looks like there are more houses built on the second half of the range of the graph (1960-2022). It shows an average increase throughout the years.

```{r code 2}
ggplot(ames_clean, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_point()
```

To better see the relationship, I adjusted the Sale Price axis. 

```{r code 3}
ggplot(ames_clean, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_point() +
  coord_cartesian(ylim = c(0, 750000))
```

Generally, it seems like sales price increases with the year the house is built. So new houses in Ames generally have higher sale prices.
The oddities seen in step 3 can be seen in the first plot, as some outlier values are seen for very high sale prices. These outliers are around year 2000, following the trend that newer houses usually have higher sale prices.

### Sebastian's Work:
